---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warnings = FALSE)
knitr::opts_chunk$set(results = "asis")

```

```{r, echo = FALSE, warning=FALSE}
load(file = "data.RData")
library(RISmed)
library(lubridate)
library(knitr)
library(pander)
authors = paste0("(", 1:nrow(authors), ")", authors$LastName, " ", authors$Initials)
authors = paste(authors, collapse = ", ")
similar_articles = data.frame(Id = sim_id, Title = sim_titles)
```
**`r id`**   `r journal``r ifelse(is.na(year), "", paste0(", ", year))` `r ifelse(is.na(month), "", as.vector(lubridate::month(label = TRUE, month)))` `r ifelse(is.na(day), "", day)` (`r ifelse(is.na(issue), "", issue)` `r ifelse(is.na(volume), "", paste("vol.", volume))`)
  
Authors: `r authors`  
  
Affiliations: `r affiliation`  
  
## Title: `r title`  

`r format(text, scientific = FALSE)`

`r paste("PMID:", PMID, "[PubMed - indexed for MEDLINE]")`

`r ifelse(exists("citations"), paste("Number of citations:", citations), "")`

```{r}
pandoc.table(similar_articles, split.cells = c(5,65))
```

